On the numerical instability of Gaussian wave packets

### 2017-04-28 semii.tex
phase space grids and regularisation

>>>>

(Insert figures from phasegrid below.)

It turns out that the steps of the integration formula quickly become larger than the state vector.  This can be solved by Tychonov conditioning.  Constraining~$dc$ to be orthogonal to~$c$ doesn't help, because~$dc$ is too large for the small angle approximations to work, and this does not keep the norm constant.

The matrix~$〈A⁺|H|A〉$ is not normal.  However, because~$|A〉〈A⁺|≈1$, the coefficient vectors~$〈A⁺|E_i〉$ are very nearly eigenvectors, with eigenvalues~$E_i$.  The approximation is very good for low energy, but starts to fail as the energy~$E_i$ approaches the highest energy in the span of $|A〉$.  Presumably the eigenvectors are those of the projection of~$H$ on to the span of~$|A〉$.

If~$〈A⁺|$ is Tychonov regularised, then the same argument should work on the low energy space where the regularised expansion is a good approximation.  But it doesn't appear to: eigenvalues of~$H$ are shifted that are low enoug that the corresponding singular vectors of~$A$ should hardly be touched by regularisation.

Todo.  For number states~$|n〉 with energies~$E_n$, see how the size of~$〈A⁺|n〉$ varies with the lagrange multiplier.
